Measuring Perceptions and Preferences for Meritocracy

### 2021-09-02 paper.Rmd
chunks
- hide chunks

#------ extract factor loadings ------#
loads01<- data.frame(round(inspect(fs1_o,what="std")$lambda,digits = 3))
loads01[loads01==c(0.00)] <- NA; names(loads01) <- c(paste0("M1.",1:4))

>>>>

#------ extract factor loadings ------#
loads01<- data.frame(round(lavaan::inspect(fs1_o,what="std")$lambda,digits = 3))
loads01[loads01==c(0.00)] <- NA; names(loads01) <- c(paste0("M1.",1:4))
